\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2023-01-04 ms/adult.tex
Update ms

\setcounter{page}{0}

@@

\begin{abstract}
\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture. Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online. We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts. The median American Internet user today spends X minutes per month consuming pornography, visiting Y sites per month; the 95th percentile is X and Y respectively. Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume about as much pornography online as Republicans.
\end{abstract} 
\clearpage
\doublespace

@@

In this paper, we investigate how much pornography Americans consume online. Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography. The median American Internet user spends X minutes per month (Y\% of their time online) consuming pornography, visiting Y unique sites; the 95th percentile for time spent consuming pornography online is YY minutes.

@@

\section*{Data}\label{sec:data}
We use passively observed browsing data from a YouGov survey to measure the consumption of adult content. YouGov maintains a large online panel recruited through a variety of methods. It uses matched sampling to survey respondents: The provider first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey. For details and validation, see \citet{rivers2009}. For this particular sample, panelists also provided de-identified access to their web browsing activity via passive metering software installed voluntarily on their computers. The software, called RealityMine, captures visited web URLs independent of the type of browser or browser-specific privacy settings.

The data are from 1,200 respondents and contains a month of data from June, 2022.  We have data on visits to domains, which are about 6 million in total. For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.

@@

\section*{Measuring Pornographic Content}
We code pornographic content at the domain level. Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as porn sites. These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains. Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites. For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We manually check the top adult domains in our sample to remove obvious false positives of porn sites. Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}

@@

\subsection*{Consumption of Pornography}
The consumption of pornography is highly concentrated. Traffic to the top 10 most frequented porn sites is more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}). Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site (\cref{fig:concentration_porn_consumption}).  The next most frequented pornographic site constitutes less than 20 percent of total traffic.

@@

\subsection*{Partisan Differences in Consumption of Pornography Online}

@@

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[ht]
\centering
\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
\includegraphics[width=.6\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
}
\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party}
	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}. The Internet has dramatically increased access to pornography. This leads to the concern that pornography consumption has become very widespread. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little.

The second contribution of our paper is estimates of partisan differences in consumption of pornography online. Both the parties claim the higher ground when it comes to women--- one's case for morality is steeped in religion, the other's in enduring concern for women. Our data suggest that the partisan differences are likely very small.

@@

\subsection{Skew in Consumption of Pornographic Content}

%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

%=====================================================================
% Tabulated percentiles of proportion of duration spent on adult sites
%=====================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites}
	\label{tab:distribution_prop_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_prop_duration} for the plot.
	}
\end{table}

\section{Partisan Differences}
\subsection{Distribution of Differences}
%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

\subsection{Accounting for Confounders}

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
		Given the skew in consumption of pornography, we also performed tests for difference in means for the measures of pornography consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
	}
\end{table}

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
	\label{tab:characteristics_split_by_porn_consumers}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
		These 65 individuals are not substantially different in characteristics than those included in the sample (see \textbf{TABLE ??}).
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
	}
\end{table}

>>>>

@@

\thispagestyle{empty}
\begin{abstract}
\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture. Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online. We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts. The median American Internet user today spends X minutes per month consuming pornography, visiting Y sites per month; the 95th percentile is X and Y respectively. Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume about as much pornography online as Republicans.
\end{abstract} 
\clearpage
\setcounter{page}{1}
\doublespace

@@

In this paper, we investigate how much pornography Americans consume online. Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography. Most individuals in the sample do not consumer pornography.
The median American Internet user spends 0 minutes per month consuming pornography (0\% of their time online), visiting 122 unique sites. 
The median American consumer of pornography spends about 44 minutes per month consuming pornography (3\% of their time online), visiting three unique pornographic sites. 
The 95th percentile for time spent consuming pornography online is 337 minutes (about 21\% of their time online).

@@

\section*{Data}\label{sec:data}
We use passively observed browsing data from a YouGov survey to measure the consumption of adult content \citep{data-dataverse}. YouGov maintains a large online panel recruited through a variety of methods. It uses matched sampling to survey respondents: The provider first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey. For details and validation, see \citet{rivers2009}. For this particular sample, panelists also provided de-identified access to their web browsing activity via passive metering software installed voluntarily on their computers. The software, called RealityMine, captures visited web URLs independent of the type of browser or browser-specific privacy settings.

The data are from 1,200 respondents and contains a month of data from June, 2022.  We have data on visits to domains, which are about 6 million in total. For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain. 
We capture about 64k unique sites, of which 900 are pornographic sites (1.4\$ of sites).

@@

\section*{Measuring Pornographic Content}
We code pornographic content at the domain level. Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as porn sites. These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites. See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains. Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites. For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.} \footnote{We manually check the top adult domains in our sample to remove obvious false positives of porn sites. Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}

@@

\subsection*{Consumption of Pornography}
The consumption of pornography is highly concentrated. Traffic to the top 10 most frequented porn sites is more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site, a behavior that is fairly consistent across parties (\cref{fig:concentration_porn_consumption_topX_by_party}). The next most frequented pornographic site constitutes less than 20 percent of total traffic.

@@

\subsection*{Partisan Differences in Consumption of Pornography Online}
%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

@@

Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}. The Internet has dramatically increased access to pornography. This leads to the concern that pornography consumption has become very widespread. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.

The second contribution of our paper is estimates of partisan differences in consumption of pornography online. Both the parties claim the higher ground when it comes to women---one's case for morality is steeped in religion, the other's in enduring concern for women. Our data suggest that the partisan differences are likely very small.

@@

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Porn Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

\FloatBarrier
\subsection{Skew in Consumption of Pornographic Content}
%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

%=====================================================================
% Tabulated percentiles of proportion of duration spent on adult sites
%=====================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites}
	\label{tab:distribution_prop_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_prop_duration} for the plot.
	}
\end{table}

\FloatBarrier
\section{Partisan Differences}
\subsection{Distribution of Differences}
%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

\FloatBarrier
\subsection{Accounting for Confounders}
%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
		Given the skew in consumption of pornography, we also performed tests for difference in means for the measures of pornography consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
	}
\end{table}

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
	\label{tab:characteristics_split_by_porn_consumers}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
	}
\end{table}
